---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fledgingr: An R Bindings Of [Sudachi.rs](https://github.com/WorksApplications/sudachi.rs)

<!-- badges: start -->
<!-- badges: end -->

This is an experimental R package to provide an interface to sudachi.rs, a Rust implementation of Sudachi.
Under the hood, this package is powered by [extendr framework](https://extendr.github.io/) to bridge between R and Rust.

## Why fledgingr?

fledging = 巣立ち (sudachi)

## Prior work

* [uribo/sudachir](https://github.com/uribo/sudachir)

## Installation

You can install the development version of fledgingr from r-universe:

``` r
install.packages("fledgingr",
  repos = c(
    yutannihilation = "https://yutannihilation.r-universe.dev",
    CRAN = "https://cloud.r-project.org"
  )
)
```

## Usages

```{r}
library(fledgingr)

x <- c(
  "真実をお伝えしていきます",
  "高輪ゲートウェイ駅"
)

tokenize(x)
```

You can change the mode. By default, `"C"` is chosen.

```{r}
tokenize("選挙管理委員会", mode = "A")$surface
tokenize("選挙管理委員会", mode = "B")$surface
tokenize("選挙管理委員会", mode = "C")$surface
```

## Licenses

In addition to depend on sudachi.rs, the fledgingr package copies the several
code from sudachi.rs' repository, which is licensed under the Apache-2.0 license.

* The Rust code here is basically based on [the implementation of the CLI tool][1]
* The files under `inst/sudachi_resources` are copied from [`resources` directory on the repository][2]

[1]: https://github.com/WorksApplications/sudachi.rs/blob/ad1f15818536a379c668ea48fcebaca2278df38e/sudachi-cli/src/main.rs
[2]: https://github.com/WorksApplications/sudachi.rs/tree/develop/resources
