---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fledgingr: An R Bindings Of [Sudachi.rs](https://github.com/WorksApplications/sudachi.rs)

<!-- badges: start -->
<!-- badges: end -->

This is an experimental R package to provide an interface to sudachi.rs, a Rust implementation of Sudachi.
Under the hood, this package is powered by [extendr framework](https://extendr.github.io/) to bridge between R and Rust.


The Rust code here is based mainly on [this CLI tool](https://github.com/WorksApplications/sudachi.rs/blob/ad1f15818536a379c668ea48fcebaca2278df38e/sudachi-cli/src/main.rs) on
the sudachi.rs repository, which is licensed under Apache-2.0 License.

## Why fledgingr?

fledging = 巣立ち (sudachi)

## Prior work

* [uribo/sudachir](https://github.com/uribo/sudachir)

## Installation

You can install the development version of fledgingr:

``` r
devtools::install_github("yutannihilation/fledgingr")
```

## Example

```{r}
library(fledgingr)

# Download the dictionary from https://github.com/WorksApplications/SudachiDict
Sys.setenv(SUDACHI_DICT_PATH = "~/Downloads/sudachi-dictionary-20210802/system_full.dic")

x <- c(
  "今日もあなただけにニンジャの真実をお伝えしていきます",
  "高輪ゲートウェイ駅"
)

knitr::kable(tokenize(x))
```

```{r}
# Change mode
tokenize("選挙管理委員会", mode = "A")$surface
tokenize("選挙管理委員会", mode = "B")$surface
tokenize("選挙管理委員会", mode = "C")$surface
```

